---
name: Tanya
surname: Strydom
#profilepic: "profile.png"
position: "PhD Student"
address: "Département de sciences biologiques, Université de Montréal"
#phone: +46 76 567 8299
www: "tanyadoesscience.com"
email: "tanya.strydom@umontreal.ca"
twitter: TanyaS_08
github: TanyaS08
orcid: 0000-0001-6067-1349
#aboutme: "Cheese"
#googlescholar: AkDd5u8AAAAJ
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua"]
nocite: '*@' # don't change this if you want to print out all the refs
csl: apa-cv.csl # change this if you want to use other citation styles
knit: (function(inputFile, encoding) {
     rmarkdown::render(inputFile,
    output_file = "cv",
     encoding = encoding, 
     output_dir = "~/Documents/TanyaDoesScience/static/files");
     rmarkdown::render(inputFile,
    output_file = "cv",
     encoding = encoding, 
     output_dir = "docs/")
     })
    
---

```{r setup, include=FALSE, echo=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble);library(rorcid)
```

# Research Interests

computational ecology; functional traits; ecological networks; machine learning; FAIR and open science

# Education

```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(tibble)
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy: Biological Sciences","Advisor: T. Poisot, PhD", "2020 - Present", "Université de Montréal", "Montréal, Canada",
  "Doctor of Philosophy: Biological Sciences","Thesis: Machine learning in ecology", "2020 - Present", "Université de Montréal", "Montréal, Canada",
  "Master of Science: Ecology and Biodiversity","Advisor: K. Hylander, PhD", "2018-20", "Stockholms Universitet", "Stockholm, Sweden",
  "Master of Science: Ecology and Biodiversity","Thesis: Declines and increases in northern and southern plant populations after changes in the microclimate", "2018-20", "Stockholms Universitet", "Stockholm, Sweden",
  "Bachelor of Science (Honours): Plant Sciences","Advisor: P.C. le Roux, PhD", "2017", "University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science (Honours): Plant Sciences","Thesis: Bush encroachment in South Africa’s montane grasslands: the impact of Leucosidea sericea on microclimate and vegetation", "2017", "University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science: Ecology", NA, "2014-16", "University of Pretoria", "Pretoria, South Africa"
) %>%
  detailed_entries(with=Degree, when=Year, what=Institution, where=Where, why=Advisor)
```

# Research Experience

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~ Project, ~Supervisor, ~Description, ~ Year,
  #For PFTC
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Attended the 5th Plants Functional Traits Course in Peru co-hosted by the Univesity of Bergen and Arizona University.", "2020",
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Theory on plant functional traits and their relationships with broader ecological processes.", "2020",
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Practical elements include: experimental design, data collection and curation, and report writing.", "2020",
  #For MSc
  "Plant vital rates along microclimate gradients.", "K. Hylander, PhD","Masters degree research project.", "2019-20",
  "Plant vital rates along microclimate gradients.", "K. Hylander, PhD","Focused on the variation of plant population vital rates along microclimate gradients and the role of historic climatic conditions.", "2019-20",
  #For interactions
  "Plant-pollinator interactions in different microsites", "J. Ehrlén, PhD and A. Tack, PhD", "A Masters level course research project.", "2019",
  "Plant-pollinator interactions in different microsites", "J. Ehrlén, PhD and A. Tack, PhD", "Independently worked on hypothesis formulation and experimental design.", "2019",
    #For marion
    "Changes in plant functional traits at fine-scales", "P.C. le Roux, PhD", "Collecting and processing plant functional traits on sub-Antarctic Marion Island.", "2018",
  "Changes in plant functional traits at fine-scales", "P.C. le Roux, PhD", "Research focused on looking at changes in plant functional traits along microclimate gradients.", "2018",
  #Honours
  "The impact of an encroaching species on vegetation and microclimate", "P.C. le Roux, PhD","Honours degree research project.", "2017",
  "The impact of an encroaching species on vegetation and microclimate", "P.C. le Roux, PhD","Research focused on the concepts of biotic interactions, ecosystem engineering and habitat modification.", "2017") %>% 
  detailed_entries(with=Project, when=Year, why=Description, what = Supervisor)


```


\newpage
# Technical Skills

\begin{cvskills}
  \cvskill
    {Statistical Analysis}
    {generalized and linear mixed-effect models; mulitvariate analysis; Bayesian analysis; primarily using R}

  \cvskill
    {Spatial Analysis}
    {spatial analysis in ecology; ArcGIS; Maxent; GBIF}
    
  \cvskill
    {Image Analysis}
    {ImageJ; Adobe Photoshop}
    
  \cvskill
    {Phylogenetic Analysis}
    {extracting and cleaning samples from GenBank; MEGA}
    
  \cvskill
    {Academic Writing}
    {assessed at various levels; peer-reviewed articles; literature reviews; research proposals; reports; popular articles}

  \cvskill
    {Oral Communication}
    {masters level course; presented in various settings}

  \cvskill
    {Peer Review}
    {as an assistant (PLoS ONE, 2018); second-round reviewer (Plant Ecology, 2019)}

  \cvskill
    {Language Skills}
    {English and Afrikaans as a native speaker; conversational in German; basic Swedish and Spanish}

\end{cvskills}

# Written Work

## PEER-REVIEWED
```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("pubs.bib")

```

## MANUSCRIPTS

**Under Review**

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("Under_Review.bib")

```

**In Prep**

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("In_prep.bib")

```

## POPULAR ARTICLES

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("Popular_Articles.bib")

```

$^\clubsuit$ = should be considered equal lead

# Talks

## INVITED TALKS

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~ Title, ~Points, ~ Year, ~ Conference, ~ Where,
  "Taking FAIR and open science to the field: The evolution of the PFTC field course","Presented alongside Aud, H. Halbritter", "Oct. 13, 2020", "Living Norway Colloquium 2020", "NINA, Norway"
) %>%
  detailed_entries(with=Title, when=Year, what=Conference, where=Where, why=Points)

```

\newpage

# Internships

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
  'University of Bergen',  "UiB Internship", "2020", "Website development for the Plants Functional Courses website. This included content creation as well as some front end development",
  'University of Pretoria',  "3rd year Undergraduate Mentorship Program", "2016", "Worked as an assistant within the M. Robertson lab. This included the sorting and identification of pitfall trap samples as well as extracting information from databases"
) %>% 
  detailed_entries(
    what = Institution,
    with = Title, 
    when = Year,
    why = Job
  )

```


# Funding and Awards

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
  'Awarded by: University of Pretoria',  "Qualified for the UP Postgraduate Masters Research Bursary.", "2018",
  'Awarded by: University of Pretoria',  "Awarded the 3rd year Undergraduate Mentorship Bursary.", "2016"
) %>% 
  detailed_entries(
    what = Institution,
    with = Award, 
    when = Year
  )

```

