---
name: Tanya
surname: Strydom
profilepic: "profile.png"
#position: "Professor"
#address: "School of Physics & Chemistry, École Normale Supérieure"
phone: +46 (0)76 567 8299
www: "tanyadoesscience.com"
email: "tanya.strydom@icloud.com"
twitter: TanyaS_08
github: TanyaS08
orcid: 0000-0001-6067-1349
#google scholar: AkDd5u8AAAAJ
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
csl: ecology.csl # change this if you want to use other citation styles
nocite: '*@' # don't change this if you want to print out all the refs
docname: Ecosystem Stability PhD Position
knit: (function(inputFile, encoding) {
    rmarkdown::render(inputFile,
    output_file = "ApplicationPackage_TS",
     encoding = encoding, output_dir = "docs/")
  })
    
---

```{r setup, include=FALSE, echo=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble);library(rorcid)
```

\vspace{7mm}

Dear Kevin Wilcox,  

This position will examine the drivers of plant community and ecosystem stability at a variety of spatial and temporal scales. The student will learn to incorporate empirical findings into process-based and hierarchical models. Dissertation subject matter is flexible and will depend on student’s interests and affinities. Training and mentorship will be available in study design, ecological sampling, and process-based modeling. Student will be based at the University of Wyoming, and field research will likely be in US grassland ecosystems.

INTRODUCTION

Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test 

RESEARCH INTERESTS

Broadly I am interested in the factors that play a role in shaping communities, more so how species respond to and interact with their environment and neighbouring species. I find this especially interesting at fine scales and am particularly interested in the role of the microclimate and niche construction in shaping species responses and interactions. With regards to species responses I am interested in how these may be manifested as variation in trait expression or as changes in species interactions.
A topic that I find of particular interest is the role of phenotypic plasticity in allowing a species to persist in an area and as a result how trait expression may vary among different microhabitats or along environmental gradients and how this in turn may alter the importance or nature of species interactions. I am also interested in how we can use this information with regards to improving our understanding species distributions and our ability to model them. However, there are other avenues of research that I have always found interesting and would love to gain more exposure to, such as looking at the bigger, phylogenetic, picture or how pairwise interactions fit together to form networks within the community and the importance of indirect interactions. I believe that improving our understanding of these relationships may prove beneficial in understanding how a species may respond in a changing world.
I enjoy projects that have a strong field component that find their basis in observational studies as I believe that it is often difficult to emulate the nuances of real world conditions using a strictly experimental approach. However, I do believe that there is value in working with quasi-experimental designs in natural settings. In addition, I would love to work with a project that has a temporal component to it and tracks species/individuals in time not just in space (due to the limited time available for honours and masters projects I have only worked with the spatial component of environmental variation). I have an inclination towards and enjoy the analytical and programming side of research as well and have done multiple statistical courses including a PhD-level course focusing on Bayesian statistics. I am very interested in further developing this skillset by implementing them within an ecoinformatic framework by conducting research that is focused on the building of usable models and furthering the development of ecological theories. I would like to broaden my skillset as a researcher and am interested in potentially applying my research interests in systems that I have previously had limited exposure to, this includes potentially working with plant-animal interactions or solely with animals as a way to expand on the plant-focused research I have previously conducted. 
 

TRAINING



WHY INTERESTED IN THIS POSITION

Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test

CONCLUSIONS

Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test Some test 

\vspace{7mm}

Best Regards, 

\includegraphics{Signature-copy.jpg}

Tanya Strydom  

\newpage

# Curriculum Vitae

# Research Interests

functional traits; ecoinformatics; microclimates; species interactions; FAIR and open science

# Education

```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(tibble)
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Master of Science: Ecology and Biodiversity","Advisor: K. Hylander, PhD", "2018-20", "Stockholm University", "Stockholm, Sweden",
  "Master of Science: Ecology and Biodiversity","Thesis: Thesis: Declines and increases in northern and southern plant populations after changes in the microclimate", "2018-20", "Stockholm University", "Stockholm, Sweden",
  "Bachelor of Science (Honours): Plant Sciences","Advisor: P.C. le Roux, PhD", "2017", "University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science (Honours): Plant Sciences","Thesis: Thesis: Bush encroachment in South Africa’s montane grasslands: the impact of Leucosidea sericea on microclimate and vegetation", "2017", "University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science: Ecology", NA, "2014-16", "University of Pretoria", "Pretoria, South Africa"
) %>%
  detailed_entries(with=Degree, when=Year, what=Institution, where=Where, why=Advisor)
```

# Research Experience

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~ Project, ~Supervisor, ~Description, ~ Year,
  #For PFTC
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Attended the 5th Plants Functional Traits Course in Peru co-hosted by the Univesity of Bergen and Arizona University.", "2020",
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Theory on plant functional traits and their relationships with broader ecological processes.", "2020",
  "Plant functional trait responses to elevation and fire","V. Vandvik, PhD and B.J. Enquist, PhD", "Practical elements include: experimental design, data collection and curation, and report writing.", "2020",
  #For MSc
  "Plant vital rates along microclimate gradients.", "K. Hylander, PhD","Masters degree research project.", "2019-20",
  "Plant vital rates along microclimate gradients.", "K. Hylander, PhD","Focused on the variation of plant population vital rates along microclimate gradients and the role of historic climatic conditions.", "2019-20",
  #For interactions
  "Plant-pollinator interactions in different microsites", "J. Ehrlén, PhD and A. Tack, PhD", "A Masters level course research project.", "2019",
  "Plant-pollinator interactions in different microsites", "J. Ehrlén, PhD and A. Tack, PhD", "Independently worked on hypothesis formulation and experimental design.", "2019",
    #For marion
    "Changes in plant functional traits at fine-scales", "P.C. le Roux, PhD", "Collecting and processing plant functional traits on sub-Antarctic Marion Island.", "2018",
  "Changes in plant functional traits at fine-scales", "P.C. le Roux, PhD", "Research focused on looking at changes in plant functional traits along microclimate gradients.", "2018",
  #Honours
  "The impact of an encroaching species on vegetation and microclimate", "P.C. le Roux, PhD","Honours degree research project.", "2017",
  "The impact of an encroaching species on vegetation and microclimate", "P.C. le Roux, PhD","Research focused on the concepts of biotic interactions, ecosystem engineering and habitat modification.", "2017") %>% 
  detailed_entries(with=Project, when=Year, why=Description, what = Supervisor)


```

# Skillset

\begin{cvskills}
  \cvskill
    {Statistical Analysis}
    {generalized and linear mixed-effect models; mulitvariate analysis; Bayesian analysis; primarily using R}

  \cvskill
    {Spatial Analysis}
    {spatial analysis in ecology; ArcGIS; Maxent; GBIF}
    
  \cvskill
    {Image Analysis}
    {ImageJ; Adobe Photoshop}
    
  \cvskill
    {Phylogenetic Analysis}
    {Extracting and cleaning samples from GenBank; MEGA}
    
  \cvskill
    {Academic Writing}
    {assessed at various levels; peer-reviewed articles; literature reviews; research proposals; reports; popular articles}

  \cvskill
    {Oral Communication}
    {masters level course; presented in various settings}

  \cvskill
    {Peer Review}
    {as an assistant (PLoS ONE, 2018); second-round reviewer (Plant Ecology, 2019)}

  \cvskill
    {Website Development}
    {content creation; front-end development (Adobe Illustrator/HTML/CSS/R Markdown)}
    
  \cvskill
    {Language Skills}
    {English and Afrikaans as a native speaker; conversational in German; basic Swedish and Spanish}

\end{cvskills}

\newpage

# Written Work

## PEER-REVIEWED
```{r, echo=FALSE, message = FALSE, warning = FALSE}

library(dplyr)

scholar::get_publications("AkDd5u8AAAAJ", flush = TRUE) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), year) %>% 
  mutate(doi = "10.1111/gcb.14904") %>%
  RefManageR::as.BibEntry() %>% 
  RefManageR::WriteBib("Published.bib")

bibliography_entries("Published.bib")

```

## MANUSCRIPTS

**Under Review**

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("Under_Review.bib")

```

**In Prep**

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("In_prep.bib")

```

## POPULAR ARTICLES

```{r, echo=FALSE, message = FALSE, warning = FALSE}

bibliography_entries("Popular_Articles.bib")

```

# Internships

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
  'University of Bergen',  "UiB Internship", "2020", "Website development for the Plants Functional Courses website. This included content creation as well as some front end development",
  'University of Pretoria',  "3rd year Undergraduate Mentorship Program", "2016", "Worked as an assistant within the M. Robertson lab. This included the sorting and identification of pitfall trap samples as well as extracting information from databases"
) %>% 
  detailed_entries(
    what = Institution,
    with = Title, 
    when = Year,
    why = Job
  )

```


# Funding and Awards

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
  'Awarded by: University of Pretoria',  "Qualified for the UP Postgraduate Masters Research Bursary.", "2018",
  'Awarded by: University of Pretoria',  "Awarded the 3rd year Undergraduate Mentorship Bursary.", "2016"
) %>% 
  detailed_entries(
    what = Institution,
    with = Award, 
    when = Year
  )

```

# References

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~Name, ~Title, ~Contact, ~Number,
  'Peter C. le Roux, Ph.D.',  "Assistant professor of Ecology and Biodiversity, University of Pretoria", "peter.leroux@up.ac.za", "+27 (0)12 420 6761",
  'Kristoffer Hylander, Ph.D.',  "Professor of Ecolgy,  Department of Ecology, Environment and Plant Sciences, Stockholm University", "kristoffer.hylander@su.se", NA,
  'Sehoya Cotner, Ph.D.',  "Professor of Biology Teaching and Learning, University of Minnesota", "sehoya@umn.edu", "+1 (612) 626 2385"
) %>% 
  detailed_entries(
    where = Contact,
    with = Name, 
    what = Title,
    when = Number
  )
```