---
#citeproc: no
graphics: no
name: Brian S.
surname: Maitner
headcolor: FF10F0
qualifications: "PhD"
#pronouns: he/him/his
position: "Postdoctoral Researcher"
address: "Department of Geography, Department of Environment and Sustainability, University at Buffalo, Buffalo, New York, USA"
phone: +1 (616) 856 0780
#profilepic: LogoNetwork.png
#www: ""
email: "bmaitner@gmail.com"
twitter: BrianMaitner
github: bmaitner
orcid: 0000-0002-2118-9880
googlescholar: GVb9deIAAAAJ
researchgate: Brian-Maitner
#aboutme: |
date: "`r format(Sys.time(), '%B %Y')`"
csl: "../csl/apa7-cv.csl"
nocite: "@*"
bibliography:
  journals: "../bib/journal.bib"
  review: "../bib/under_review.bib"
  popular: "../bib/popular_articles.bib"
header-includes:
  - \usepackage{fontawesome5}
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(fontawesome)
```

# Research Interests

Biodiversity; global change; community assembly; coexistence; community phylogenetics; behavioral ecology; community ecology; tropical ecology; invasion biology; biogeography; niche conservatism; trait-based ecology; data science; geospatial analyses; ecoinformatics; R

# Professional Experience

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Position, ~Additional, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral Scholar","Research focused on developing workflows to inform land managers in the Cape Floristic Region of South Africa of potential changes in vegetation (e.g. fires, droughts, invasive species, illegal land clearing).", "2021-present", "University of Buffalo", "Buffalo, NY, USA",
    "Postdoctoral Scholar","The workflow utilized remote sensing data, hierarchical Bayesian modeling to predict NDVI over time and detect deviations, and machine learning for classifying deviation from expectations into land change categories.", "2021-present", "University of Buffalo", "Buffalo, NY, USA",
  "Terrestrial sampling stratification designer","As part of NASA’s first biodiversity-focused program, BIOSCAPE (https://www.bioscape.io/ ), I led the selection of the terrestrial sites that would be used by BIOSCAPE.", "2022-present", "BIOSCAPE", NA,
  "Terrestrial sampling stratification designer","Sites were selected by analyzing and synthesizing multiple environmental variables to ensure sites were representative while also being compatible with project logistics and goals (e.g., near roads, publicly accessible, small slope, etc.)", "2022-present", "BIOSCAPE", NA,
  "Postdoctoral Scholar","Research focused on using unsupervised clustering algorithms to conduct novel delineations of global ecoregions on the basis of global plant distribution models, assessing their conservation status, and projecting future changes.", "2020-2021", "University of Connecticut", "Storrs, CT, USA"
) %>%
  detailed_entries(with=Position, when=Year, what=Institution, where=Where, why=Additional,
                   .protect = FALSE)

```

# Education

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}
library(tibble)
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy: Ecology and Evolutionary Biology","Advisor: B.J. Enquist, PhD", "2014-2020", "University of Arizona", "Tucson, AZ, USA",
  "Doctor of Philosophy: Ecology and Evolutionary Biology","Thesis: Challenging current paradigms in communirt phylogenestics: Including source range phylogenetic structure and transforming pylogenetic branches to reflect trait evolution.", "2014-2020", "University of Arizona", "Tucson, AZ, USA",
  "Master of Science: Ecology and Evolutionary Biology","Advisor: K. Hylander, PhD", "2009-2013", "Rice University", "Houston, TX, USA",
  "Master of Science: Ecology and Evolutionary Biology","Thesis: Declines and increases in northern and southern plant populations after changes in the microclimate", "2009-2013", "Rice University", "Houston, TX, USA",
  "Bachelor of Science: Zoology","High Honors", "2004-2006", "Michigan State University", "East Lansing, MI, USA",
  "Bachelor of Science: Zoology","Concentrations in General Zoology and Ecology, Evolution, and Organismal Biology", "2004-2006", "Michigan State University", "East Lansing, MI, USA",
  "Bachelor of Science: Ecology", NA, "2001-2004", "Grand Rapids Community College", "Grand Rapids, MI, USA"
) %>%
  detailed_entries(with=Degree, when=Year, what=Institution, where=Where, why=Advisor,
                   .protect = FALSE)
```

# Additional Education and Relevant Travel

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~ Project, ~Supervisor, ~Description,  ~ Year,
  "iDiv Summer School",NA,"German Centre for Integrative Biodiversity Research", "2017",
  "Computation Ecology Summer School",NA,"University of Montreal", "2016",
  "Biomedical Responsible Conduct of Research, Basic Course",NA, "Collaborative Institutional Training Initiative", "2012",
  "Species Distribution Modeling Training Course",NA,"American Museum of Natural History", "2011",
  "Studies in Natural History: Costa Rica",NA,"Grand Rapids Community College", "2003 & 2004",
  "Studies in Natural History: Canada",NA,"Grand Rapids Community College", "2003") %>%
  detailed_entries(with=Project, what=Description, when=Year,why = Supervisor)

```

# Funding

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
    'Awarded by: British Ecological Society',  "Robert May Prize", "2022",
  'Awarded by: University of Pretoria',  "Qualified for the UP Postgraduate Masters Research Bursary", "2018",
  'Awarded by: University of Pretoria',  "Awarded the 3rd year Undergraduate Mentorship Bursary", "2016",
) %>%
  detailed_entries(
    what = Institution,
    with = Award,
    when = Year
  )

```

# Publications

<!--- 
\textbf{\textsuperscript{*}} Indicates co-lead author

\vspace{\baselineskip}
## **Preprints**

::: {#refs-review}
:::

\vspace{\baselineskip}
## **Publications**

::: {#refs-journals}
:::

\vspace{\baselineskip}
## **Software Packages**

::: {#refs-journals}
:::

<!--- 
\newpage
--->


# Presentations
\vspace{\baselineskip}
## **Invited talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
 "Phylogenetic relationships and community assembly.","2011", "Grand Rapids Community College", "\\textbf{Maitner, B.S.}",
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```
\vspace{\baselineskip}
## **Talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "The Ecosystem Monitoring and Management Application (EMMA) Workflow: Automating Change Detection and Reporting in the Hyperdiverse Fynbos of South Africa.", "2022", "American Geophysical Union Conference", "\\textbf{Maitner, B.S.}, Slingsby, J., Moncrieff, G.R., Hu, Y., Ma, Y., Wilson, A.",
  "Forecasting vegetation dynamics in an open ecosystem by integrating deep learning and environmental variables.", "2022", "American Geophysical Union Conference", "Hu, Y., Ma, Y., Moncrieff, G.R., Slingsby, J., Wilson, A., \\textbf{Maitner, B.S.}, Zhenqi, R.Z. ",
  "BioFI - The Biodiversity Forecasting Initiative to Understand Population, Community, and Ecosystem Function Under Climate Change.", "2022", "American Geophysical Union Conference", "Enquist, B.J., Merow, C., Nikolopoulos, E., Frazier, A., Duncanson, L., Anagnostou, E., Boyle, B., Breshears, D.D., Ernst, K.C., Foden, W., Gallagher, R.V., Klausmeier, C.A., Litchman, E., Norberg, J., Marquet, P.A., \\textbf{Maitner, B.S.}, Midgley, G., Pascual, M., Rominger, A., Savage, V., Silander, J., Slingsby, J., Svenning, J.C., Wilson, A., Dietze, M., Cavender-Bares, J., Roehrdanz, P., Hannah, L..",
  "Forecasting future global biodiversity: Predicting current and future global plant distributions, community structure, and ecosystem function.", "2019", "American Geophysical Union Conference", "\\textbf{Maitner, B.S.}"
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Short Presentations and Posters**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Phylogenetic scaling and community phylogenetic patterns.", "2018", "Ecological Society of America Conference", "\\textbf{Maitner, B.S.}, Enquist, B.J.",
  "Evolutionary imbalance dominates phylogenetic patterns in successful bird introductions.", "2018", "Ecological Society of America Conference", "\\textbf{Maitner, B.S.}, Dlugosch, K.M, Enquist, B.J.",
  "Quantifying species tolerances and functional diversity using n-dimensional hypervolumes: a comparison of methods.", "2017", "International Biogeography Society Conference", "Morrow, C. B., Blonder, B., \\textbf{Maitner, B.S.}, Lamanna, C., Kerkhoff, D., Enquist, B.J.",
  "Comparative community phylogenetics.", "2016", "Gordon Conference: Unifying Ecology Across Scales", "\\textbf{Maitner, B.S.}, Enquist, B.J.",
  "Phylogenetic diversity-area relationships reveal macroecological patterns.", "2015", "Ecological Society of America Conference", "\\textbf{Maitner, B.S.}, Morlon, H., Enquist, B.J.",
  "Are mountain passes higher in the tropics? A community phylogenetic approach.", "2012", "Ecological Society of America Conference", "Roy, C.L., \\textbf{Maitner, B.S.}, Dunham, A.E.",
  "Nest Defense and Parental Investment in the House Wren.", "2012", "Wilson Ornithological Society Conference", "Fox, K., Caffarelli A., Walters L., \\textbf{Maitner, B.S.}",
  " Phylogenetic distance and bird invasions.", "2010", "Ecological Society of America Conference", "\\textbf{Maitner, B.S.} Rudgers J.A., Dunham A.E., Whitney K.D."
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Workshops and Organized Sessions**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Open data in the life sciences: Challenges and Opportunities.", "2017", "OpenCon",NA,
  "Integrating and cleaning biodiversity data: Workflows to model ranges and merge associated ecological, phylogenetic, and trait information.", "2017", "International Biogeography Society Conference",NA
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

# Referee Duties

Acta Oecologica; American Journal of Botany; Annals of Botany; Biodiversity and Conservation; Biological Conservation; Biotropica; Diversity and Distributions; Ecography; Ecology; Ecological Informatics; Ecology Letters; Frontiers of Biogeography; Global Ecology and Biogeography; iScience; Journal of Biogeography; Journal of Ecology; Journal of Vegetation Science; Journal of the Arkansas Academy of Science; Methods in Ecology and Evolution; Nature Communications; New Phytologist; Philosophical Transactions of the Royal Society B; PLOS ONE; Science of the Total Environment; Scientific Reports.


# Fellowships and Grants

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year, 
  'University of Arizona',  "Galileo Circle Scholarship", "2019-2020",
  "University of Arizona", "William A. Calder III Memorial Scholarship", "2019",
  'University of Bergen',  "TransPlant Fellowship", "2019",
  'University of Arizona',  "Data Science Ambassadorship", "2018",
  'University of Arizona', "Libraries’ scholarship to attend OpenCo", "2017",
  'Rice University', "Graduate fellowship", "2009-2013",
  'Rice University', "Rice Centennial Award to Support Undergraduate Research", "2012"
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year,
    .protect = FALSE
  )

```


# Awards

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year,
    
  'Ecography',  "E4 Award (nominated)", "2021",
  "University of Arizona", "Graduate Award for Outstanding Teaching", "2020",
  'Global Biodiversity Information Facility',  "Ebbe Nielsen Challenge (Second place)", "2019",
  'Rice University',  "Award for Best Graduate Paper", "2012-2013",
  'Rice University',  "Peter Savvas Nelson Award", "2012-2013",
  'Rice University',  "Joe Davies Prize for Outstanding Service as a Teaching Assistant", "2009-2010",
  'Michigan State University',  "Dean's list", "2004-2006",
  'Grand Rapids Community College',  "Foundation Scholarship", "2004-2005",
  NA,  "Hansen Environmental Scholarship", "2004",
  "Grand Rapids Community College",  "Biology Student of the Year (nominated)", "2004",
  'Grand Rapids Community College',  "Dean's list", "2002-2004",
  NA,  "Michigan Merit Award", "2002"
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year,
    .protect = FALSE
  )

```

# Teaching Experience

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
    
  'University of Arizona',  "Introduction to Agent Based and Individual Based Models (ECOL596W)", "2019", "Proposed, designed and implemented course",
  'University of Arizona',  "Adaptive Evolution and Biodiversity Lab (BIO 182L)", "2018-2019", "Instructor",
  'University of Arizona',  "Adaptive Evolution and Biodiversity Lab (BIO 182L)", "2015-2016", "Instructor",
  'Rice University',  "Scientific Communication (EBIO 412)", "2012", "Teaching Assistant",
  'Rice University',  "Biological Diversity Lab (EBIO 327)", "2011", "Teaching Assistant",
  'Rice University',  "Animal Behavior (EBIO 321)", "2010-2011", "Teaching Assistant",
  'Rice University',  "Conservation Biology (EBIO 323)", "2010", "Teaching Assistant"
) %>%
  detailed_entries(
    where = Institution,
    with = Title,
    when = Year,
    what = Job,
    .protect = FALSE
  )

```

# Student Mentorship

# Service/Outreach

# Community Engagement
\vspace{\baselineskip}
## **Science Communication**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year,
  "Fortnightly cartoonist for Ecology for the Masses blog",  "Cartoonist", "2020 - 2022",
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year
  )

```
\vspace{\baselineskip}
## **Popular Articles**

<!--- 
::: {#refs-popular}
:::
--->

<!--chapter:end:CV.Rmd-->
