---
#citeproc: no
graphics: yes
name: Tanya
surname: Strydom
#headcolor: 414141
#qualifications: "BSc. (Hons), MSc."
position: "PhD Candidate"
address: "Département de sciences biologiques, Université de Montréal - Campus MIL, 1375 Ave.Thérèse-Lavoie-Roux, Montréal, QC H2V 0B3, Canada"
#phone: +46 76 567 8299
profilepic: LogoNetwork.png
www: "tanyadoesscience.com"
email: "tanya.strydom@umontreal.ca"
twitter: TanyaS_08
github: TanyaS08
orcid: 0000-0001-6067-1349
#publons: ABH-3144-2020
#googlescholar: AkDd5u8AAAAJ
#researchgate: Tanya-Strydom
#aboutme: |
date: "`r format(Sys.time(), '%B %Y')`"
csl: "../csl/apa7-cv.csl"
nocite: "@*"
headcolor: 529FA8 # use love symbol #2
knit: (function(inputFile, encoding) {
     rmarkdown::render(inputFile,
    output_file = "cv",
     encoding = encoding,
     output_dir = "~/Documents/TanyaDoesScience/static/files");
     rmarkdown::render(inputFile,
    output_file = "cv",
     encoding = encoding)
     })
bibliography_journals: "../bib/journal.bib"
bibliography_review: "../bib/under_review.bib"
bibliography_popular: "../bib/popular_articles.bib"
bibliography_prep: "../bib/in_prep.bib"
header-includes:
  - \usepackage{fontawesome5}
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(fontawesome)
```

# Research Interests

computational ecology; functional traits; ecological networks; species interactions; FAIR and open science

# Education

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}
library(tibble)
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy: Biological Sciences","Advisor: T. Poisot, PhD", "2020 - Present", "Université de Montréal", "Montréal, Canada",
  "Doctor of Philosophy: Biological Sciences","Thesis: Decoding Ecological Networks (in terms of the information from within)", "2020 - Present", "Université de Montréal", "Montréal, Canada",
  "Master of Science: Ecology and Biodiversity","Advisor: K. Hylander, PhD", "2018-20", "Stockholms Universitet", "Stockholm, Sweden",
  "Master of Science: Ecology and Biodiversity","Thesis: Declines and increases in northern and southern plant populations after changes in the microclimate", "2018-20", "Stockholms Universitet", "Stockholm, Sweden",
  "Bachelor of Science (Honours): Plant Sciences","Advisor: P.C. le Roux, PhD", "2017", "University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science (Honours): Plant Sciences","Thesis: Bush encroachment in South Africa’s montane grasslands: the impact of \\textit{Leucosidea sericea} on microclimate and vegetation", "2017",
"University of Pretoria", "Pretoria, South Africa",
  "Bachelor of Science: Ecology", NA, "2014-16", "University of Pretoria", "Pretoria, South Africa"
) %>%
  detailed_entries(with=Degree, when=Year, what=Institution, where=Where, why=Advisor,
                   .protect = FALSE)
```

# Fellowships and Internships

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
  'Computational Biodiversity Science and Services  (BIOS\\textsuperscript{2}) training program',  "BIOS\\textsuperscript{2} Fellow", "2021 - present", NA,
  'University of Bergen',  "UiB Internship", "2020", "Website development for the Plants Functional Courses website. This included content creation as well as some front end development",
  'University of Pretoria',  "3rd year Undergraduate Mentorship Program", "2016", "Worked as an assistant within the M. Robertson lab. This included the sorting and identification of pitfall trap samples as well as extracting information from databases"
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year,
    why = Job,
    .protect = FALSE
  )

```

# International Collaboration and Working Groups

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~ Project, ~Supervisor, ~Description,  ~ Year,
  # CAN metaweb
  "Canadian metaweb construction working group","PIs: T. Poisot (Université de Montréal) and L.J. Pollock, (McGill University)","Leader of one of the sub-projects focused on using machine learning for prediction", "2021",
  # Network pred synth
  "Network prediction synthesis working group","PIs: T. Poisot (Université de Montréal) and L.J. Pollock, (McGill University)","Co-lead author of resulting publication", "2020",
  #PFTC5
  "Plant Functional Trait Course 5 in Peru","PIs: V. Vandvik (University of Bergen) and B.J. Enquist, (University of Arizona)","Plant functional responses to fire", "2020") %>%
  detailed_entries(with=Project, why=Description, when=Year, what = Supervisor)


```


\newpage

# Publications

\textsuperscript{*} Indicates co-lead author

\vspace{\baselineskip}
## **Publications**
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_journals}
:::
\endgroup
\vspace{\baselineskip}
## **Preprints**

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_review}
:::
\endgroup

\newpage

# Presentations
\vspace{\baselineskip}
## **Invited talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~Points, ~ Year, ~ Conference, ~ Where,
  "Taking FAIR and open science to the field: The evolution of the PFTC field course","Presented as part of the education and open science workshop", "Oct., 2020", "Living Norway Colloquium 2020: Towards openess and transparency in applied ecology", "Virtual",
  "Taking FAIR and open science to the field: The evolution of the PFTC field course","\\textbf{Tanya Strydom} alongside Aud H. Halbritter, 109 PFTC Participants", "Oct., 2020", "Living Norway Colloquium 2020: Towards openess and transparency in applied ecology", "Virtual",
) %>%
  detailed_entries(with=Title, when=Year, what=Conference, where=Where, why=Points,
    .protect = FALSE)

```
\vspace{\baselineskip}
## **Talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Exploring the complexity of ecological networks using SVD entropy", "Dec., 2020", "11th Annual QCBS Symposium", "\\textbf{Tanya Strydom}, Giulio V. Dalla Riva and Timothée Poisot",
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Short Presentations**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~Points, ~ Year, ~ Conference, ~ Where,
  "Reconstructing food webs using transfer learning","\\textbf{Tanya Strydom}, Salomé Bouskila and Timothée Poisot", "Aug., 2021", "CSEE-SCEE 2021 Annual Meeting", "Virtual",
  # "Reconstructing food webs using transfer learning",'\\href{https://tanyas08.github.io/Talks/2020_Dec_QCBS/index.html}{Link to twitter thread}', "Aug., 2021", "CSEE-SCEE 2021 Annual Meeting", "Virtual"
) %>%
  detailed_entries(with=Title, when=Year, what=Conference, where=Where, why=Points,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Workshops**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~Points, ~ Year, ~ Conference, ~ Where,
  "Designing a collective prototype of future tropical and subtropical science","Gracielle Higino, Mickey Boakye, Norma Forero, \\textbf{Tanya Strydom}", "Jul., 2021", "ATBC Annual Meeting", "Virtual",
) %>%
  detailed_entries(with=Title, when=Year, what=Conference, where=Where, why=Points,
    .protect = FALSE)

```

<!--- 
# Teaching
\vspace{\baselineskip}
## **Workshops**

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

tribble(
  ~ Title, ~Points, ~ Year, ~ Conference, ~ Where,
  "(un)Reproducibility Detox - Package and Dependency Management","Gracielle Higino, Andrew MacDonald, \\textbf{Tanya Strydom}", "Nov., 2021", "BIOS$^2$", "Virtual"
) %>%
  detailed_entries(with=Title, when=Year, what=Conference, where=Where, why=Points,
    .protect = FALSE)

```

--->

# Science Communication & Engagement
\vspace{\baselineskip}
## **Communication**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year,
  "Fortnightly cartoonist for Ecology for the Masses blog",  "Cartoonist", "2020 - present",
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year
  )

```
\vspace{\baselineskip}
## **Popular Articles**

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_popular}
:::
\endgroup

\newpage

# Academic Service


```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
  'Member',  "Societry for Open, Reliable, and Transparent Ecology and Evolutionary Biology", "2021 - Present",
    'Student Member',  "Québec Centre for Biodiversity Sciences", "2020 - Present",
  'Plant Ecology, PLoS ONE',  "Reviewed Journals", "",
) %>%
  detailed_entries(
    what = Institution,
    with = Award,
    when = Year
  )

```

# Funding and Awards

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
  'Awarded by: University of Pretoria',  "Qualified for the UP Postgraduate Masters Research Bursary", "2018",
  'Awarded by: University of Pretoria',  "Awarded the 3rd year Undergraduate Mentorship Bursary", "2016"
) %>%
  detailed_entries(
    what = Institution,
    with = Award,
    when = Year
  )

```

<!--chapter:end:CV.Rmd-->
