---
#citeproc: no
graphics: no
name: Brian S.
surname: Maitner
headcolor: FF10F0
qualifications: "PhD"
#pronouns: he/him/his
position: "Postdoctoral Researcher"
address: "Department of Geography, Department of Environment and Sustainability, University at Buffalo, Buffalo, New York, USA"
phone: +1 (616) 856 0780
#profilepic: LogoNetwork.png
#www: ""
email: "bmaitner@gmail.com"
twitter: BrianMaitner
github: bmaitner
orcid: 0000-0002-2118-9880
googlescholar: GVb9deIAAAAJ
researchgate: Brian-Maitner
#aboutme: |
date: "`r format(Sys.time(), '%B %Y')`"
csl: "../csl/apa7-cv.csl"
nocite: "@*"
bibliography:
  journals: "../bib/journal.bib"
  review: "../bib/under_review.bib"
  popular: "../bib/popular_articles.bib"
header-includes:
  - \usepackage{fontawesome5}
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = TRUE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(fontawesome)
```

# Research Interests

Biodiversity; global change; community assembly; coexistence; community phylogenetics; behavioral ecology; community ecology; tropical ecology; invasion biology; biogeography; niche conservatism; trait-based ecology; data science; geospatial analyses; ecoinformatics; R

# Professional Experience

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Position, ~Additional, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral Scholar","Research focused on developing workflows to inform land managers in the Cape Floristic Region of South Africa of potential changes in vegetation (e.g. fires, droughts, invasive species, illegal land clearing).", "2021-present", "University of Buffalo", "Buffalo, NY, USA",
    "Postdoctoral Scholar","The workflow utilized remote sensing data, hierarchical Bayesian modeling to predict NDVI over time and detect deviations, and machine learning for classifying deviation from expectations into land change categories.", "2021-present", "University of Buffalo", "Buffalo, NY, USA",
  "Terrestrial sampling stratification designer","As part of NASA’s first biodiversity-focused program, BIOSCAPE (https://www.bioscape.io/ ), I led the selection of the terrestrial sites that would be used by BIOSCAPE.", "2022-present", "BIOSCAPE", NA,
  "Terrestrial sampling stratification designer","Sites were selected by analyzing and synthesizing multiple environmental variables to ensure sites were representative while also being compatible with project logistics and goals (e.g., near roads, publicly accessible, small slope, etc.)", "2022-present", "BIOSCAPE", NA,
  "Postdoctoral Scholar","Research focused on using unsupervised clustering algorithms to conduct novel delineations of global ecoregions on the basis of global plant distribution models, assessing their conservation status, and projecting future changes.", "2020-2021", "University of Connecticut", "Storrs, CT, USA"
) %>%
  detailed_entries(with=Position, when=Year, what=Institution, where=Where, why=Additional,
                   .protect = FALSE)

```

# Education

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}
library(tibble)
tribble(
  ~ Degree, ~Advisor, ~ Year, ~ Institution, ~ Where,
  "Doctor of Philosophy: Ecology and Evolutionary Biology","Advisor: B.J. Enquist, PhD", "2014-2020", "University of Arizona", "Tucson, AZ, USA",
  "Doctor of Philosophy: Ecology and Evolutionary Biology","Thesis: Challenging current paradigms in communirt phylogenestics: Including source range phylogenetic structure and transforming pylogenetic branches to reflect trait evolution.", "2014-2020", "University of Arizona", "Tucson, AZ, USA",
  "Master of Science: Ecology and Evolutionary Biology","Advisor: K. Hylander, PhD", "2009-2013", "Rice University", "Houston, TX, USA",
  "Master of Science: Ecology and Evolutionary Biology","Thesis: Declines and increases in northern and southern plant populations after changes in the microclimate", "2009-2013", "Rice University", "Houston, TX, USA",
  "Bachelor of Science: Zoology","High Honors", "2004-2006", "Michigan State University", "East Lansing, MI, USA",
  "Bachelor of Science: Zoology","Concentrations in General Zoology and Ecology, Evolution, and Organismal Biology", "2004-2006", "Michigan State University", "East Lansing, MI, USA",
  "Bachelor of Science: Ecology", NA, "2001-2004", "Grand Rapids Community College", "Grand Rapids, MI, USA"
) %>%
  detailed_entries(with=Degree, when=Year, what=Institution, where=Where, why=Advisor,
                   .protect = FALSE)
```

# Additional Education and Relevant Travel

```{r, echo=FALSE, message = FALSE, warning = FALSE}
tribble(
  ~ Project, ~Supervisor, ~Description,  ~ Year,
  "iDiv Summer School",NA,"German Centre for Integrative Biodiversity Research", "2017",
  "Computation Ecology Summer School",NA,"University of Montreal", "2016",
  "Biomedical Responsible Conduct of Research, Basic Course",NA, "Collaborative Institutional Training Initiative", "2012",
  "Species Distribution Modeling Training Course",NA,"American Museum of Natural History", "2011",
  "Studies in Natural History: Costa Rica",NA,"Grand Rapids Community College", "2003 & 2004",
  "Studies in Natural History: Canada",NA,"Grand Rapids Community College", "2003") %>%
  detailed_entries(with=Project, what=Description, when=Year,why = Supervisor)

```

# Funding

```{r, echo=FALSE, message = FALSE, warning = FALSE}

tribble(
  ~Institution, ~Award, ~Year,
    'Awarded by: British Ecological Society',  "Robert May Prize", "2022",
  'Awarded by: University of Pretoria',  "Qualified for the UP Postgraduate Masters Research Bursary", "2018",
  'Awarded by: University of Pretoria',  "Awarded the 3rd year Undergraduate Mentorship Bursary", "2016",
) %>%
  detailed_entries(
    what = Institution,
    with = Award,
    when = Year
  )

```

# Publications

<!--- 
\textbf{\textsuperscript{*}} Indicates co-lead author

\vspace{\baselineskip}
## **Preprints**

::: {#refs-review}
:::

\vspace{\baselineskip}
## **Publications**

::: {#refs-journals}
:::

\vspace{\baselineskip}
## **Software Packages**

::: {#refs-journals}
:::

<!--- 
\newpage
--->


# Presentations
\vspace{\baselineskip}
## **Invited talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
    "What's [complexity] got to do with it?","Jul., 2023", "NetSci 2023", "\\textbf{Tanya Strydom}",
  "Making something out of nothing at all: Transfer learning for network prediction","Apr., 2022", "ML4MS mini-conference", "\\textbf{Tanya Strydom}",
 "Taking FAIR and open science to the field: The evolution of the PFTC field course","Oct., 2020", "Living Norway Colloquium", "\\textbf{Tanya Strydom} alongside Aud H. Halbritter, 109 PFTC Participants",
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```
\vspace{\baselineskip}
## **Talks**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Exploring the complexity of ecological networks using SVD entropy", "Dec., 2020", "11th Annual QCBS Symposium", "\\textbf{Tanya Strydom}, Giulio V. Dalla Riva and Timothée Poisot",
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Short Presentations and Posters**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Reconstructing food webs using transfer learning", "Aug., 2021", "CSEE-SCEE Annual Meeting", "\\textbf{Tanya Strydom}, Salomé Bouskila and Timothée Poisot",
  #QCBS POSTER
  "Food web reconstruction using transfer learning", "Dec., 2021", "12th Annual QCBS Symposium", "\\textbf{Tanya Strydom}, Salomé Bouskila and Timothée Poisot",
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\vspace{\baselineskip}
## **Workshops and Organized Sessions**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~ Title, ~ Year, ~ Conference, ~ Who,
  "Space Oddity: Thinking About Ecological Networks Across Space", "Aug., 2022", "ESA/CSEE Meeting","Francis Banville, Gabriel Dansereau, \\textbf{Tanya Strydom}",
  "Designing a collective prototype of future tropical and subtropical science", "Jul., 2021", "ATBC Annual Meeting","Gracielle Higino, Mickey Boakye, Norma Forero, \\textbf{Tanya Strydom}"
) %>%
  detailed_entries(with=Title, when=Year, what=Who, where=Conference,
    .protect = FALSE)

```

\newpage

# Referee Duties

Acta Oecologica; American Journal of Botany; Annals of Botany; Biodiversity and Conservation; Biological Conservation; Biotropica; Diversity and Distributions; Ecography; Ecology; Ecological Informatics; Ecology Letters; Frontiers of Biogeography; Global Ecology and Biogeography; iScience; Journal of Biogeography; Journal of Ecology; Journal of Vegetation Science; Journal of the Arkansas Academy of Science; Methods in Ecology and Evolution; Nature Communications; New Phytologist; Philosophical Transactions of the Royal Society B; PLOS ONE; Science of the Total Environment; Scientific Reports.


# Fellowships and Grants

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
    
  'Computational Biodiversity Science and Services  (BIOS\\textsuperscript{2}) training program',  "BIOS\\textsuperscript{2} Fellow", "2021 - present", NA,
  # LIVING DATA
  "Canadian Institute of Ecology and Evolution, Birds Canada", "Living Data Internship", "2022", "Data archiving for the Piping Plovers conservation project",
  'University of Bergen',  "UiB Internship", "2020", "Website development for the Plants Functional Courses website. This included content creation as well as some front end development",
  'University of Pretoria',  "3rd year Undergraduate Mentorship Program", "2016", "Worked as an assistant within the M. Robertson lab. This included the sorting and identification of pitfall trap samples as well as extracting information from databases"
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year,
    why = Job,
    .protect = FALSE
  )

```


# Awards

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year, ~Job,
    
  'Computational Biodiversity Science and Services  (BIOS\\textsuperscript{2}) training program',  "BIOS\\textsuperscript{2} Fellow", "2021 - present", NA,
  # LIVING DATA
  "Canadian Institute of Ecology and Evolution, Birds Canada", "Living Data Internship", "2022", "Data archiving for the Piping Plovers conservation project",
  'University of Bergen',  "UiB Internship", "2020", "Website development for the Plants Functional Courses website. This included content creation as well as some front end development",
  'University of Pretoria',  "3rd year Undergraduate Mentorship Program", "2016", "Worked as an assistant within the M. Robertson lab. This included the sorting and identification of pitfall trap samples as well as extracting information from databases"
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year,
    why = Job,
    .protect = FALSE
  )

```




# Teaching Experience

# Service/Outreach

# Community Engagement
\vspace{\baselineskip}
## **Science Communication**

```{r, echo=FALSE, message = FALSE, warning = FALSE, results='asis'}

tribble(
  ~Institution, ~Title, ~Year,
  "Fortnightly cartoonist for Ecology for the Masses blog",  "Cartoonist", "2020 - 2022",
) %>%
  detailed_entries(
    what = Institution,
    with = Title,
    when = Year
  )

```
\vspace{\baselineskip}
## **Popular Articles**

<!--- 
::: {#refs-popular}
:::
--->

<!--chapter:end:CV.Rmd-->
